% Based (but completely redesigned) on Resume in Latex Template by Sourabh Bajaj
\documentclass[letterpaper, 11pt]{article}

\pdfgentounicode=1

% font
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{noto}

% packages
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{scrextend}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{enumitem}

\usepackage[left=1.25cm,right=1.25cm,top=2cm,bottom=2cm]{geometry}

% custom

% command macros
\newcommand{\iconSpace}{\hspace{1px}}
\newcommand{\bulletSpace}{\vspace{-8pt}}
\newcommand{\hSpace}{\hspace{8px}}
\newcommand{\secStartSpace}{\vspace{3pt}}
\newcommand{\secEndSpace}{\vspace{5pt}}
\newcommand{\spaceCollapse}{\vspace{-5pt}}
% use the macro for work experience header
% arg 1 = header title
% arg 2 = position title (subtitle (in italics)
% arg 3 = date
\newcommand{\workHeader}[3]{
\noindent \textbf{#1} \hfill \textbf{#3}\\
	\textit{#2}
}

% line spacing
% \linespread{1.15}

% colors
\definecolor{blue}{RGB}{14, 100, 237} % change the blue color if this one is not to your liking

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=blue,
    urlcolor=blue,
}

% indent space
\titlespacing{\section}{0pt}{1px}{2ex}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

% ------------- header ------------- %
\begin{center} 
	{\Large \textbf{Sukhpreet Singh}}\\
	\vspace{1px}
	% "footnotes" (icon + link)
	{\footnotesize
		\faicon{envelope} \href{mailto:joesmith@gmail.com}{sukh.singhlotey@gmail.com} 
		\hSpace
		\faicon{globe} \iconSpace \href{https://sukhlotey.github.io/imSukhpreet/}{Sukhpreet Singh} 
		\hSpace 
		\faicon{linkedin} \hspace{.1px} \href{https://www.linkedin.com/in/sukhpreetlotey/}{Linkedin} 
		\hSpace
		}\\
	{\footnotesize
		\faicon{github} \iconSpace \href{https://github.com/sukhlotey}{Github}
		\hSpace 
		\faicon{phone} \iconSpace
		+91 7696138519
		% \hSpace 
		% \faicon{map-marker} \iconSpace
		% Regina, SK
	}
\end{center}
\spaceCollapse
% ------------- end header ------------- %


% ------------- education ------------- %
\section{\color{blue} \textbf{Education}}
\secStartSpace

\begin{addmargin}[1em]{1em}
\textbf{Guru Nanak Dev Engineering College} \hfill \textbf{2023 - 2025}\\
        \setlength\parindent{1cm} Master of Computer Application (MCA)\\
	\textbf{Ludhiana College of Engineering & Technology} \hfill \textbf{2020 - 2023}\\
	\setlength\parindent{1cm} B.Sc. Information Technology (IT)\\
        \textbf{Senior Secondary Education (Non-Medical(Science))}\hfill \textbf{2018 - 2020}\\
        \setlength\parindent{1cm} Dasmesh Senior Secondary School\\
        \textbf{  Matriculation }\hfill \textbf{2017 - 2018}\\
        \setlength\parindent{1cm} Dasmesh Senior Secondary School\\
\end{addmargin}
\secEndSpace
% ------------- end education ------------- %


% ------------- work experience ------------- %
\section{\color{blue} \textbf{Executive Summary}}
\secStartSpace
As a MERN stack developer, I specialize in building web applications using MongoDB, Express.js, React.js, and Node.js. With expertise in both front-end and back-end technologies, I design and implement robust, scalable solutions that meet clients' needs. My proficiency extends from database management to user interface development, ensuring seamless functionality and a great user experience. I'm passionate about staying updated with the latest trends and technologies in web development to deliver cutting-edge solutions.
\newline
\secEndSpace

% ------------- end experience ------------- %


% ------------- projects ------------- %

\section{\color{blue} \textbf{Projects}}
\secStartSpace

\begin{addmargin}[1em]{1em}
% ------------- project 1 ------------- %
\noindent\href{https://github.com/sukhlotey/Expense-Management-System}{\textbf{Expense Management System}}  \hfill \textbf{January 2024} 
		
	\noindent The Mern Stack Application for Expenses
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Packages:} Nodejs,Expressjs,ReactJs,MongoDB,Nodemon,JWT Token,Morgan,Moment Packages
		      \bulletSpace
		\item Source: \faicon{github} \href{https://github.com/sukhlotey/Expense-Management-System}{\underline{EMS}}
	\end{itemize}
		
	% ------------- end project 1 ------------- %
 \noindent\href{https://github.com/sukhlotey/Uptime-monitor}{\textbf{Uptime Monitor}}  \hfill \textbf{January 2024} 
		
	\noindent The Mern Stack Application Uptime Monitor
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Packages:} Nodejs,Expressjs,ReactJs,MongoDB,Nodemon,JWT Token,Winston,Nodemailer,Moment Packages
		      \bulletSpace
		\item Source: \faicon{github} \href{https://github.com/sukhlotey/Uptime-monitor}{\underline{Uptime Monitor}}
	\end{itemize}
		%........%
	\noindent\href{https://github.com/sukhlotey/newsdaily}{\textbf{News Man}}  \hfill \textbf{November 2023} 
		
	\noindent The React application that shows world's live news
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Tools:} React,News api, JavaScript,Bootstrap, CSS
		      \bulletSpace
        
		\item Source: \faicon{github} \href{https://github.com/sukhlotey/newsdaily}{\underline{News Man}}
	\end{itemize}
%.....%
 \noindent\href{https://github.com/sukhlotey/invoice-set}{\textbf{Invoice Set}}  \hfill \textbf{November 2023} 
		
	\noindent The Invoice set Application that generate invoice
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Tools:} React,JavaScript,React-Bootstrap
		      \bulletSpace
            	\item working demo: \faicon{globe} \href{https://invoiceset.netlify.app/}
  {\underline{Invoice Set}}
		\item Source: \faicon{github} \href{https://github.com/sukhlotey/invoice-set}
  {\underline{Invoice Set}}
	\end{itemize}
	
	% ------------- project 2 ------------- %
 \newpage
	\noindent\href{https://github.com/sukhlotey/think-pedia}{\textbf{Think Pedia}}  \hfill \textbf{March 2022} 
		
	\noindent The React application that shows you wikipedia results with better way through Think Pedia
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Tools:} React,Wikipedia api, JavaScript, CSS
		      \bulletSpace
		\item working demo: \faicon{globe} \href{https://thinkpedia.netlify.app/}{\underline{Think Pedia}}
           \item Source: \faicon{github} \href{https://github.com/sukhlotey/think-pedia}{\underline{Think Pedia}}
	\end{itemize}
	% ------------- end project 2 ------------- %
		% ------------- project 3 ------------- %
	\noindent\href{https://github.com/sukhlotey/imSukhpreet}{\textbf{Portfolio}}  \hfill \textbf{December 2021} 
		
	\noindent My Personal Website with contacts and social media handles.
	\spaceCollapse
	\begin{itemize}
		\item \textbf{Technology/Tools:} JavaScript, CSS, HTML
		      \bulletSpace
		\item working demo: \faicon{globe} \href{https://sukhlotey.github.io/imSukhpreet/}{\underline{Portfolio}}
           \item Source: \faicon{github} \href{https://github.com/sukhlotey/imSukhpreet}{\underline{Portfolio}}
	\end{itemize}
	% ------------- end project 2 ------------- %
		
\end{addmargin}
\secEndSpace
% ------------- end projects ------------- %
\section{\color{blue} \textbf{Experience}}
\secStartSpace


\begin{addmargin}[1em]{1em}
	\setstretch{1.125}
\noindent \textbf{Training at Ryazio Pvt.ltd} 
\\
I received specialized training in the MERN stack with TypeScript at Ryazio Pvt Ltd, gaining expertise in building full-stack web applications. This program provided in-depth knowledge of MongoDB, Express.js, React, and Node.js, along with TypeScript's strong typing capabilities. I learned to develop scalable and maintainable applications, focusing on efficient database management, server-side logic, client-side interfaces, and seamless integration across the stack. This training has significantly enhanced my ability to deliver high-quality, type-safe web solutions.
\\
\noindent \textbf{Training at Step GNE} 
\\
I received comprehensive training in ReactJS at Step GNE Institute, where I developed a strong foundation in building dynamic, responsive web applications. The course covered key concepts such as component-based architecture, state management, hooks, and effective integration with APIs. This training has equipped me with the skills to create robust, scalable applications and enhanced my proficiency in modern web development practices.
\end{addmargin}
\secEndSpace

% ------------- skills ------------- %
\section{\color{blue} \textbf{Skills}}
\secStartSpace

\begin{addmargin}[1em]{1em}
	\setstretch{1.125}
	\noindent \textbf{Technologies i work in:} Html5, CSS, SASS, JavaScript, Bootstrap, Tailwind CSS, Material UI,React Redux Toolkit, TypeScript, ReactJS, NodeJS, ExpressJs, MongoDB, UI Tools, npm, yarn \\
	\noindent \textbf{OS:} Linux, MS Windows\\
	\noindent \textbf{Tools:} Visual Studio Code, Sublime,Git
\end{addmargin}
\secEndSpace
% ------------- end skills ------------- %


% ------------- achievements ------------- %
\section{\color{blue} \textbf{Achievements}}
\secStartSpace

\begin{addmargin}[1em]{1em}
	\begin{itemize}[itemsep=-2.25pt]
		\item \textbf{Hackathon 2023} 
  \href{https://sukhlotey.github.io/imSukhpreet/Images/hackathon.pdf}{\underline{certificate}} \hfill \textbf{2023}
  \newline
    \secStartSpace
  Winning the hackathon was a testament to our team's dedication and innovative spirit. With relentless determination, we crafted a cutting-edge sports management system that promises to revolutionize how sports events are organized and managed. From seamless registration processes to real-time analytics, our solution stands as a beacon of efficiency and convenience.
  \secEndSpace
  
		\item \textbf {Hacktoberfest 2022 \& 2023} \hfill  \textbf{2022 \& 2023}
\newline
\secStartSpace
Recipient of the prestigious Hacktoberfest award for outstanding contributions to open source software development. Demonstrated expertise in collaborating with global developer communities and delivering high-impact contributions to multiple projects. Recognized for dedication, innovation, and leadership in the field of software engineering.
\secEndSpace
  
\end{itemize}
\end{addmargin}
% ------------- end achievements ------------- %


% \documentclass{article}

% \begin{document}
% % End of automatically added code

% Automatically added code
\end{document}
% End of automatically added code